---
title: "R Workshop Capstone Report"
subtitle: "Training track, attendance and post-training assessment scores"
author: "Facilitator-reviewed example"
format:
  html: default
  docx: default
  pdf: default
execute:
  echo: true
  warning: false
  message: false
---

```{r}
#| label: setup
library(tidyverse)
library(broom)

lecturers <- read_csv("../Data/processed/anchor_dataset_clean.csv", show_col_types = FALSE) %>%
  mutate(training_track = factor(training_track, levels = c("Online", "In-Person", "Blended")))
```

## Research question

Does training track (Online, In-Person, Blended) and class attendance predict
improvement in lecturers' post-training assessment scores, after accounting
for their pre-training score? The anchor dataset is a synthetic evaluation of
a national statistics-lecturer training programme (`Data/raw/anchor_dataset.csv`).

## Data preparation

The raw dataset was imported with `readr::read_csv()` and kept untouched.
Invalid values (e.g. attendance above 100%, satisfaction outside 1-5) were
flagged and set to `NA` rather than deleted, category labels (gender, region,
institution type, training track) were standardised, and 6 exact duplicate
rows were removed using `distinct()` on `participant_id`. The full pipeline
is in `Starter-Scripts/day2_anchor_cleaning.R`; the data dictionary is in
`Data/processed/data_dictionary.csv`.

## Exploratory analysis

```{r}
#| label: fig-track-counts
#| fig-cap: "Participants by training track"
ggplot(lecturers, aes(x = training_track)) +
  geom_bar(fill = "#2C7FB8") +
  labs(x = "Training track", y = "Number of participants") +
  theme_minimal()
```

```{r}
#| label: fig-score-by-track
#| fig-cap: "Post-training score by training track"
ggplot(lecturers, aes(x = training_track, y = post_score)) +
  geom_boxplot(fill = "#FEB24C") +
  labs(x = "Training track", y = "Post-training score (0-100)") +
  theme_minimal()
```

Online was the most common track. Post-training scores appear higher, on
average, for In-Person and Blended participants than for Online participants
-- this motivates the inferential and model work below.

## Inference

```{r}
#| label: paired-test
paired_data <- lecturers %>% filter(!is.na(pre_score), !is.na(post_score))
paired_result <- t.test(paired_data$post_score, paired_data$pre_score, paired = TRUE)
mean_gain <- mean(paired_data$post_score - paired_data$pre_score)
paired_result
```

Post-training scores were on average `r round(mean_gain, 1)` points higher
than pre-training scores (paired t-test, p `r ifelse(paired_result$p.value < 0.001, "< 0.001", paste("=", round(paired_result$p.value, 3)))`).
This is both statistically and practically significant on a 0-100 scale.

## Model

```{r}
#| label: model
model_main <- lm(post_score ~ pre_score + attendance + training_track, data = lecturers)
tidy(model_main, conf.int = TRUE)
glance(model_main)$r.squared
```

Controlling for pre-training score and attendance, In-Person and Blended
participants scored higher on average than Online participants (the
reference category). Attendance was positively associated with post-training
score. The model explained roughly
`r round(glance(model_main)$r.squared * 100, 0)`% of the variance in
post-training scores. Diagnostic plots (Day 5 workbook) showed no major
violation of linearity or constant variance.

A custom OLS implementation (`Solution-Scripts/day6_manual_ols_solution.R`)
reproduced these coefficients directly from the design matrix, confirming
the regression result independently of `lm()`.

## Limitations

This is a single cross-sectional cohort with no random assignment to
training track, so the track effect should be read as an association
controlled for measured covariates, not as a causal claim. Roughly 15-20%
of rows had at least one missing value, handled here by case-wise deletion
within each model; a sensitivity analysis with multiple imputation would
strengthen the conclusion.

## Reproducibility

```{r}
#| label: session-info
sessionInfo()
```
