---
title: "R Workshop Capstone Report"
subtitle: "One-line description of your research question"
author: "Participant name"
format:
  html: default
  docx: default
  pdf: default
execute:
  echo: true
  warning: false
  message: false
---

```{r}
#| label: setup
library(tidyverse)
```

## Research question

State the capstone research question and identify the anchor dataset.

## Data preparation

Describe cleaning decisions and link to the data dictionary.

## Exploratory analysis

Include at least two interpreted figures.

## Inference

Report one inferential result (e.g. a confidence interval or hypothesis
test) linked to the research question, with assumptions and a
plain-language interpretation.

## Model

Report the fitted model addressing the research question: formula,
coefficients, uncertainty and a plain-language interpretation of the
key terms.

## Limitations

State the main limitations of the data or analysis (e.g. study design,
missingness, scope of the conclusions).

## Reproducibility

Describe the project structure and include session information.

```{r}
#| label: session-info
sessionInfo()
```
